---
title: "Vignette Title"
author: "Igor Veksler"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

One can call the graphics `hist` function on a numeric vector or numeric column such as: 
```{r, echo = TRUE, fig.width = 4, fig.height = 4}

  hist(rnorm(1000))

```

Great! Simple graphs that yield insight are beautiful. 
What about on a dataframe?  Lets take a look at the head of the `mtcars` dataframe
```{r, echo=FALSE, results='asis'}
  knitr::kable(head(mtcars, 10))
```

```{r, echo=TRUE, eval = FALSE}
  hist(mtcars)
```
##### Error: 'x' must be numeric   
:(

but wait! now with the `visualizethis` package one can just pass a dataframe and plot the histograms for all the variables. 
One can cycle through large dataframes and the function will require user input to display the next batch of graphs. 
Factors will plot barcharts by default 

```{r}
  library(visualizethis)
  hist(mtcars)
```

